Hybrid platforms and bargaining power

### 2024-06-19 src/paper/application.tex
Reshuffle appendices

Although the main reason for utilizing cooperative game theory in this model is tractability, it is by no means the only one.
This way of modelling bargaining outcomes, while uncommon, has been used to great effect in a number of other papers in the industrial organization literature \parencite[e.g.][]{montez2007downstream,hart1990property,levy1997individual,inderst2003bargaining,brugemann2019intra}.
Furthermore, it has a number of appealing properties.
For example, it is closely related to the marginal contributions of the players to the total value, and, as shown in \cref{sec:more_general_results}, it is also quite intuitive in terms of comparative statistics.
Furthermore, and perhaps more importantly, there are a number of ways to place it on non-cooperative microfoundations by setting up non-cooperative games for which the Shapley value is a subgame perfect equilibrium \parencite[e.g.][]{gul1989bargaining,hart1996bargaining,stole1996organizational}.
\Cref{sec:bargaining_microfoundation} provides an example on how this specific model can be placed on such microfoundations.
The subgame perfect equilibrium of the fully non-cooperative model described in that section coincides with the equilibrium of the bargaining model in the main text.
Therefore, one can think of the cooperative game as a more tractable representation of the one from \cref{sec:bargaining_microfoundation}.

@@

As the final, price-setting subgame is the same in both the benchmark and the bargaining model, the results in this subsection apply to both.
Discrete choice models with type I Extreme Value errors give rise to a logit-type demand function \parencite[e.g.][]{small1981applied}.
More specifically, \textcite[]{anderson2021hybrid} show that it gives rise to the following demand function.
\begin{proposition}
    \label{prop:demand_function}
    The demand for product $i$ of producer $T \in \{P, F\}$ is given by:
    \begin{align*}
        x_{T_i} = \frac{\exp\left( \frac{v_T - p_{T_i}}{\mu} \right)}{A}
    \end{align*}
    where
    \begin{align}
        A = \int_0^{N_F} \exp\left( \frac{v_F - p_{F_i}}{\mu} \right) \di + \int_0^{N_P} \exp\left( \frac{v_P - p_{P_i}}{\mu} \right) \di + 1.
        \label{eq:aggregate}
    \end{align}
\end{proposition}

@@

\subsection{Three sided bargaining }
\label{sec:two_sided}

@@

\section{More general results}
\label{sec:more_general}

While the main text examines bargaining between the platform and the entrants in the context of a specific, logit-like demand system, many of the results are more general.
This section presents those and the necessary assumptions.
The proofs for many of the propositions in the main text also rely on these more general results.

@@

Apart from the cooperative foundations, one major justification for this profit allocation rule is its intuitive behavior in terms of comparative statistics.
To illustrate this, let us examine what happens when one varies the substitutability between the fringe firms.
As it turns out, the platform's share increases if the fringe firms are more substitutable.
The following observation demonstrates this idea.
\begin{proposition}
    \label{prop:outcome_based_bargaining_power}
    Fix some $N_P, N_C \geq 0$. Let $f, \tilde{f}: \mathbb{R}^+_0 \times \mathbb{R}^+_0 \to \mathbb{R}^+_0$ two different profit functions such that $f(N_P, N_F) = \tilde{f}(N_P, N_F)$ for some $N_P, N_F$ and $f(N_P, n_F) \leq \tilde{f}(N_P, n_F)$ for all $n_F < N_F$.
    Furthermore, let us denote the corresponding platform profit shares by $\pi_P$ and $\tilde{\pi}_P$.

    Then, $\pi_P \leq \tilde{\pi}_P$.
\end{proposition}

@@

This section presents a number of results that can be derived even in this rather abstract setting.
Let us start with a technical, but very useful result.
\begin{proposition}
    \label{prop:unique_equilibrium_more_general}
    Under the conditions in \cref{ass:single_crossing}, the equilibrium is unique if it exists.
\end{proposition}
The intuition behind this result is that \cref{ass:single_crossing} ensures that the total profits achieved by the fringe is either concave or hump-shaped.
Consequently, it has at most one crossing with the -- convex and increasing -- total entry cost function (for $n_F > 0$).
This particular shape (concave or hump-shaped) is also the main driver for the later results about the comparative statics of equilibrium profits and entry.

The following two propositions are partial equilibrium results: consider the number of fringe entrants $N_F$ as fixed.
The first statement claims that the platform's profits are increasing in its own product variety.
\begin{proposition}
    \label{prop:share_of_platform}
    Assume that $f$ is continuously differentiable with respect to $N_P$ and also twice differentiable.
    Let $N_F \geq 0$.
    Then $\pi_P$ is also differentiable and
    \begin{align*}
        \frac{\partial \pi_P(N_P, N_F)}{\partial N_P} > 0.
    \end{align*}
\end{proposition}
While it might seem obvious, let us still examine what this result does and does not mean.
First, remember that $f$ is increasing in both arguments, and $N_F$ is fixed.
Therefore, an increase in $N_P$ also increases the size of the pie the participants bargain over.
This result states that the slice of the pie that the platform gets increases in this case, too.
It does not mean, however, that the \emph{relative share} of the pie that the platform gets is also bigger -- increase is only guaranteed in absolute terms.
For example, it is possible that for the new, higher value of $N_P$, the complementarities between the fringe firms become stronger, and the platform's bargaining power decreases.\footnote{
    In fact, one can show that this is the case if the cross-derivatives of $f$ are negative.
}
\cref{fig:increase_N_P_platform} shows an example of this situation.

@@

Next, let us look at an analogous result for the fringe firms.
In their case, the direction of the change depends on the complementarities between the platform and the fringe firms.
\begin{proposition}
    \label{prop:share_of_fringe}
    Assume that $f, w$ are twice continuously differentiable.
    Let $N_F > 0$.
    Then $\pi_F$ is also differentiable.
    \begin{align*}
        &\text{If } \frac{\partial^2 f(N_P, n_F)}{\partial n_P \partial n_F} < 0 \;\forall n_F \leq N_F, \text{ then } \frac{\partial \pi_F(N_P, N_F)}{\partial N_P} < 0, \\
        &\text{if } \frac{\partial^2 f(N_P, n_F)}{\partial n_P \partial n_F} > 0 \;\forall n_F \leq N_F, \text{ then } \frac{\partial \pi_F(N_P, N_F)}{\partial N_P} > 0
    \end{align*}
    for all $N_P \geq 0$.
\end{proposition}
In summary, when they are mostly substitutes (the cross-derivatives of $f$ are negative), the fringe's profits decrease as a result of an increase in $N_F$.
The intuition is that, even though the total size of the pie increases, the bargaining power of the fringe deteriorates so much that its share decreases not only in relative, but also in absolute terms (as illustrated in \cref{fig:increase_N_P_fringe}).
On the other hand, when the fringe firms are mostly complements the fringe's profits increase.

@@

Finally, let us turn to equilibrium entry as a function of the platform's product variety.
The previous proposition implies an almost immediate corollary regarding the equilibrium number of fringe entrants.
\begin{corollary}
    \label{cor:fringe_entry}
    Assume that $f, w$ are twice continuously differentiable.
    Let $N_F^*$ denote the equilibrium number of fringe firms.
    Let us also assume that $N_F^* > 0$, and that
    \begin{align*}
        \frac{\partial^2 f(n_P, n_F)}{\partial n_P \partial n_F} < 0 \quad \forall n_F \leq N_F \\
        \frac{\partial^2 f(n_P, n_F)}{\partial n_F^2} < 0 \quad \forall n_F \leq N_F.
    \end{align*}
    Then the equilibrium number of fringe firms is also differentiable and
    \begin{align*}
        \frac{\partial N_F^*}{\partial N_P} < 0.
    \end{align*}
\end{corollary}
That is, the equilibrium number of entrants increases as a response to an increase in $N_P$ if the platform and the fringe firms are complements, and decreases if they are substitutes.
The underlying reason is again the concave or hump-shaped fringe profit function.
If $N_F^*$ is an equilibrium, then fringe profits minus entry costs are strictly positive for all $N_F \leq N_F^*$ and strictly negative for all $N_F > N_F^*$.
Therefore, if an increase in $N_P$ decreases the fringe's profits for every $N_F \geq 0$, equilibrium can be restored by decreasing the number of fringe entrants, (and vice versa for the other case).
This is also related to the concept of strategic complementary and substitutability, which also depends on the cross-derivatives (i.e. the supermodularity or submodularity) of the profit function.

@@

\begin{proposition}
    \label{prop:aggregate_size_additive}
    Let $f$ have the additive form from \cref{ass:additive_profit}.
    Then
    \begin{align*}
        \frac{\partial N_F^*}{\partial N_P} < -\frac{\alpha}{\beta}.
    \end{align*}
    Furthermore,
    \begin{align*}
        \frac{\partial \Pi(N_P, N_F^*(N_P), N_C)}{\partial N_P} < 0.
    \end{align*}
\end{proposition}

\section{The platform game and the (weighted) Shapley value}
\label{sec:cooperative_game}

In this section, I describe how the profit sharing rule from \cref{ass:profit_sharing} can be derived from various cooperative games.
In each of the following subsections, I formally define a cooperative game that models the platform setting, and derive the (weighted) Shapley values of the various players.
I show that they correspond to the formulas given in \cref{ass:profit_sharing}, with a specific choice of weight functions $w_P$ and $w_F$ for each case.

\subsection{One-sided case}
\label{sec:cooperative_game_one_sided}

In the first setting, the platform and the fringe firms bargain over the total profits they generate together, and the consumers are not included in the negotiations.
The following cooperative game describes this case.

\begin{proposition}
    \label{prop:profit_sharing_one_sided}
    Consider the cooperative game above.
    Then, the Shapley values of the platform and the fringe firms are given by
    \begin{align*}
        \varphi_P(\mathcal{G}) &= \int_0^1 f(N_P, s N_F) \ds, \\
        \varphi_P(\mathcal{F}) &= \int_0^1 s N_F \partial_2 f(N_P, s N_F) \ds.
    \end{align*}
\end{proposition}

\begin{proof}[Proof of \cref{prop:profit_sharing_one_sided}]
    This result is a direct application of Proposition 3 and Corollary 2 in \textcite{stancsics2023value}.
\end{proof}

\subsection{Weighted value}
\label{sec:cooperative_game_weighted}

Now let us generalize the previous result, and assume instead that players' shares are described by their weighted values,
As before, let us start by formally describing the cooperative game.
The set of players and the characteristic function are the same as in \cref{sec:cooperative_game_one_sided}, but now the game is additionally endowed with a weight system $\mathbf{\lambda} = \{\lambda_P, \lambda_{F}(i)\}$.
Let us assume that all fringe players have the same weight $\lambda_{F}(i) \equiv 1$.

\begin{proposition}
    \label{prop:profit_sharing_weighted}
    Consider the cooperative game above.
    Then, the weighted values of the platform and the fringe firms are given by
    \begin{align*}
        \varphi_P(\mathcal{G}) &= \int_0^1 \lambda_P s ^ {\lambda_P - 1} f(N_P, s N_F) \ds, \\
        \varphi_F(\mathcal{G}) &= \int_0^1 s ^ {\lambda_P} N_F \partial_2 f(N_P, s N_F) \ds.
    \end{align*}
\end{proposition}

\begin{proof}[Proof of \cref{prop:profit_sharing_weighted}]
    This result is a direct application of Proposition 4 in \textcite{stancsics2023value}.
\end{proof}

\subsection{Two-sided case}
\label{sec:cooperative_game_two_sided}

Finally, in certain settings, it might be appropriate to assume that the consumers (or, more generally, the entities on the other side of the market) also engage in the bargaining process.
The cooperative game describing can be formalized as follows.

\section{Non-cooperative microfoundations for the bargaining outcome}
\label{sec:bargaining_microfoundation}

The model in \textcite{stole1996intra} is phrased in terms of intra-firm bargaining between the workers and the firm itself.
The workers are assumed to have a fixed outside option, and the firm is the indispensable player.
This translates directly to the platform game, with the platform being the indispensable player, and fringe firms having a zero outside option.
Furthermore, in \textcite{stole1996intra}, the bargaining outcome is interpreted as the wage for the workers.
In the current setting, this would translate to bargaining over profit shares.
However, as I argue later on, it is equivalent to bargaining over entry fees.
Finally, this section focuses on the main model, with two-sided bargaining, and the Shapley value as the equilibrium concept.
However, the same logic can be applied to the extensions presented in \cref{sec:extensions}, based on sections 3.1 and 3.2 of \textcite{stole1996intra}.

\section{Proofs and additional lemmas}
\label{sec:proofs}

\begin{lemma}
    \label{lem:single_crossing_affine_transformation}
    Let $g: \mathbb{R}^+ \to \mathbb{R}$ be a twice continuously differentiable function.
    Define
    \begin{align*}
        G(x) = \int_0^1 g(sx) \ds.
    \end{align*}
    Assume that for any $x \geq 0$, $G'(x) < 0$ or $G''(x) < 0$.

\begin{lemma}
    \label{lem:slope_at_eq}
    Let the conditions in \cref{ass:single_crossing} hold. Then for any $N_F^* > 0$ for which $\pi_F(N_P, N_F^*, N_C) = I_F N_F$, the partial derivative of fringe profits with respect to the number of fringe firms is smaller than the marginal investment cost $I_F$:
    \begin{align*}
        \left. \frac{\partial \pi_F(N_P, N_F, N_C)}{\partial N_F} \right|_{N_F = N_F^*} < I_F.
    \end{align*}
\end{lemma}
\begin{proof}[Proof of \cref{lem:slope_at_eq}]
    \cref{ass:single_crossing} states that at any $N_F \geq 0$, $\pi_F(N_P, N_F, N_C)$ is either concave or decreasing in $N_F$.
    In the remainder, let us denote partial derivatives as follows:
    \begin{align*}
        \partial_F \pi_F(N_P^*, N_F^*, N_C^*) \coloneqq \left. \frac{\partial \pi_F(N_P, N_F,  )}{\partial N_F} \right|_{N_P = N_P*, N_F = N_F^*, N_C = N_C^*}.
    \end{align*}

\begin{proof}[Proof of \cref{prop:unique_equilibrium_more_general}]
    \Cref{lem:slope_at_eq} states that for any positive $N_F^*$ for which $\pi_F(N_P, N_F^*) - N_F I_F$, the partial derivative with respect to the number of fringe firms is negative.
    Now assume by contradiction that $\exists 0 < N_F^* < N_F^{**}$ such that $\pi_F(N_P, N_F^*) = I_F N_F^*$ and $\pi_F(N_P, N_F^{**}) = I_F N_F^{**}$.
    But then the mean value theorem implies that there is a $\bar{N}_F \in (N_F^*, N_F^{**})$ such that $\partial_F \pi_F(N_P, \bar{N}_F) = I_F$.
    This is a contradiction, as $\partial_F \pi_F(N_P, N_F) < I_F$ for all $N_F^* < N_F$.
\end{proof}

\begin{proof}[Proof of \cref{prop:share_of_platform}]
    $f(N_P, N_F)$ is continuously differentiable in $N_P$, therefore the Leibniz rule can be applied to obtain
    \begin{align*}
        \frac{\partial \pi_P(N_P, N_F, N_C)}{\partial N_P} &= N_C \frac{\partial}{\partial N_P} \int_0^1 w_P(s) f(N_P, N_F) \ds \\
        &= \int_0^1 w_P(s) \underbrace{\frac{\partial f(N_P, sN_F)}{\partial N_P}}_{> 0} \ds > 0
    \end{align*}
    for any non-negative, continuous $w_P(s)$.
\end{proof}

\begin{proof}[Proof of \cref{prop:share_of_fringe}]
    Remember that
    \begin{align*}
        \pi_F(N_P, N_F, N_C) = N_C \int_0^1 w_F(s) N_F \partial_2 f(N_P, s N_F) \ds,
    \end{align*}
    By assumption, $f$ is twice continuously differentiable, therefore $\partial_2$ is also continuously differentiable in $N_P$.
    Thus, the Leibniz rule can be applied to obtain
    \begin{align*}
        \frac{\partial \pi_F(N_P, N_F, N_C)}{\partial N_P} &= \frac{\partial}{\partial N_P} N_C \int_0^1 w_F(s) N_F \partial_2 f(N_P, s N_F) \ds \\
        &= N_C \int_0^1 w_F(s) N_F \frac{\partial}{\partial N_P} \partial_2 f(N_P, s N_F) \ds \\
        &= N_C \int_0^1 w_F(s) N_F \partial^2_{12} f(N_P, s N_F) \ds.
    \end{align*}

    As $w_F(s) \geq 0$ for $s > 0$, if $\partial_2 f(N_P, s N_F)$ has the same sign over $[0, N_F]$, then the integral also has the same sign.
    Formally,
    \begin{align*}
        \forall n_F \in [0, N_F] \enspace \frac{\partial^2 f(N_P, n_F)}{\partial N_P \partial n_F} < 0 &\implies \frac{\partial \pi_F(N_P, N_F, N_C)}{\partial N_P} < 0 \\
        \forall n_F \in [0, N_F] \enspace \frac{\partial^2 f(N_P, n_F)}{\partial N_P \partial n_F} > 0 &\implies \frac{\partial \pi_F(N_P, N_F, N_C)}{\partial N_P} > 0
    \end{align*}
\end{proof}

\begin{proof}[Proof of \cref{cor:fringe_entry}]
    \Cref{prop:unique_equilibrium} establishes that if an equilibrium with $N_F > 0$ exists, it is unique.
    Use the implicit function theorem on the equation from \cref{ass:free_entry} to obtain
    \begin{align*}
        \frac{\partial N_F}{\partial N_P} = \frac{\frac{\partial \pi_F(N_P, N_F, N_C)}{\partial N_P}}{I_F - \frac{\partial \pi_F (N_P, N_F, N_C)}{\partial N_F}}
    \end{align*}
    The derivative exists if the above expression is well-defined, i.e. $\frac{\partial \pi_F (N_P, N_F, N_C)}{\partial N_F} \neq I_F$.
    Remember from \cref{prop:share_of_fringe} that the numerator of this expression is negative under the condition $\frac{\partial^2 f(N_P, N_F, N_C)}{\partial N_P \partial N_F}$.
    Now all we need to show to conclude the proof is that
    \begin{align*}
        \frac{\partial \pi_F (N_P, N_F, N_C)}{\partial N_F} < I_F,
    \end{align*}
    which is the statement of \cref{lem:slope_at_eq}.
\end{proof}

\begin{proof}[Proof of \cref{prop:aggregate_size_additive}]
    Use the implicit function theorem to get the equilibrium number of fringe firms as a function of the platform's product variety:
    \begin{align*}
        \frac{\partial N_F}{\partial N_P} = \frac{\frac{\partial \pi_F(N_P, N_F, N_C)}{\partial N_P}}{I_F - \frac{\partial \pi_F (N_P, N_F, N_C)}{\partial N_F}}.
    \end{align*}
    Remember, that from \cref{lem:slope_at_eq}, and the assumption on the investment cost function we have that $\frac{\partial \pi_F (N_P, N_F, N_C)}{\partial N_F} < I_F$.
    Then, substitute $f(N_P, N_F) = g(\alpha N_P + \beta N_P)$ into $\pi_F$ to get the following fringe profit function:
    \begin{align*}
        \pi_F(N_P, N_F, N_C) = \beta N_C N_F \int_0^1 w_F(s) g'(\alpha N_P + s \beta N_F) \ds.
    \end{align*}
    Differentiate it with respect to $N_P$ and $N_F$ and substitute into the first expression to obtain
    \begin{align*}
        \frac{\partial N_F}{\partial N_P} = \frac{
            \alpha \beta N_C N_P \int_0^1 w_F(s) g''(\alpha N_P + s \beta N_F) \ds
        }{
            \underbracket{I'_F(N_F) - \beta N_C \int_0^1 w_F(s) g'(\alpha N_P + s \beta N_F) \ds}_{(1)} - \underbracket{\beta^2 N_C N_F \int_0^1 w_F(s) s g''(\alpha N_P + s \beta N_F) \ds}_{(2)}.
        }
    \end{align*}
    From \cref{lem:slope_at_eq}, we know that the denominator of this expression is positive.
    Furthermore, the concavity of $g$ implies that expression (2) is also positive.
    Finally, from \cref{prop:share_of_fringe}, we have that the whole expression must be negative.

@@

>>>>

Although the main reason for utilizing cooperative game theory in this model is tractability, it is by no means the only one.
This way of modelling bargaining outcomes, while uncommon, has been used to great effect in a number of other papers in the industrial organization literature \parencite[e.g.][]{montez2007downstream,hart1990property,levy1997individual,inderst2003bargaining,brugemann2019intra}.
Furthermore, it has a number of appealing properties.
For example, it is closely related to the marginal contributions of the players to the total value, and, as shown in \cref{sec:more_general_results}, it is also quite intuitive in terms of comparative statics.
Furthermore, and perhaps more importantly, there are a number of ways to place it on non-cooperative microfoundations by setting up non-cooperative games for which the Shapley value is a subgame perfect equilibrium \parencite[e.g.][]{gul1989bargaining,hart1996bargaining,stole1996organizational}.
\Cref{sec:bargaining_microfoundation} provides an example on how this specific model can be placed on such microfoundations.
The subgame perfect equilibrium of the fully non-cooperative model described in that section coincides with the equilibrium of the bargaining model in the main text.
Therefore, one can think of the cooperative game as a more tractable representation of the one from \cref{sec:bargaining_microfoundation}.

@@

As the final, price-setting subgame is the same in both the benchmark and the bargaining model, the results in this subsection apply to both.
Discrete choice models with type I Extreme Value errors give rise to a logit-type demand function \parencite[e.g.][]{small1981applied}.
More specifically, \textcite[]{anderson2021hybrid} show that it gives rise to the following demand function.
\begin{proposition}
    \label{prop:demand_function}
    The demand for product $i$ of producer $T \in \{P, F\}$ is given by:
    \begin{align*}
        x_{T_i} = \frac{\exp\left( \frac{v_T - p_{T_i}}{\mu} \right)}{A}
    \end{align*}
    where
    \begin{align}
        A = \int_0^{N_F} \exp\left( \frac{v_F - p_{F_i}}{\mu} \right) \di + \int_0^{N_P} \exp\left( \frac{v_P - p_{P_i}}{\mu} \right) \di + 1.
        \label{eq:aggregate}
    \end{align}
\end{proposition}
\begin{proof}[Proof of \cref{prop:demand_function}]
    See Theorem 1 in \textcite{anderson2021hybrid}.
\end{proof}

@@

\subsection{Three sided bargaining}
\label{sec:two_sided}

@@

\section{Generalization and proofs}
\label{sec:more_general}

While the main text examines bargaining between the platform and the entrants in the context of a specific, logit-like demand system, many of the results are more general.
This section presents those and the necessary assumptions.
As the results on the main text are not proven directly, but rather derived from the general results, the proofs are also included here.

@@

Apart from the cooperative foundations, one major justification for this profit allocation rule is its intuitive behavior in terms of comparative statics.
To illustrate this, let us examine what happens when one varies the substitutability between the fringe firms.
As it turns out, the platform's share increases if the fringe firms are more substitutable.
The following observation demonstrates this idea.
\begin{proposition}
    \label{prop:outcome_based_bargaining_power}
    Assume that \cref{ass:identical_fringe,ass:monotone_profits,ass:profit_sharing} hold.
    Fix some $N_P, N_C \geq 0$. Let $f, \tilde{f}: \mathbb{R}^+_0 \times \mathbb{R}^+_0 \to \mathbb{R}^+_0$ two different profit functions such that $f(N_P, N_F) = \tilde{f}(N_P, N_F)$ for some $N_P, N_F$ and $f(N_P, n_F) \leq \tilde{f}(N_P, n_F)$ for all $n_F < N_F$.
    Furthermore, let us denote the corresponding platform profit shares by $\pi_P$ and $\tilde{\pi}_P$.

    Then, $\pi_P \leq \tilde{\pi}_P$.
\end{proposition}
\begin{proof}[Proof of \cref{prop:outcome_based_bargaining_power}]
    Immediately follows from the monotonicity of the integral.
\end{proof}

@@

This section presents a number of results that can be derived even in this rather abstract setting.
Let us start with a technical, but very useful result.
\begin{proposition}
    \label{prop:unique_equilibrium_more_general}
    Under the conditions in \cref{ass:free_entry,ass:single_crossing}, the equilibrium is unique if it exists.
\end{proposition}
\begin{proof}[Proof of \cref{prop:unique_equilibrium_more_general}]
    \Cref{lem:slope_at_eq} states that for any positive $N_F^*$ for which $\pi_F(N_P, N_F^*) - N_F I_F$, the partial derivative with respect to the number of fringe firms is negative.
    Now assume by contradiction that $\exists 0 < N_F^* < N_F^{**}$ such that $\pi_F(N_P, N_F^*) = I_F N_F^*$ and $\pi_F(N_P, N_F^{**}) = I_F N_F^{**}$.
    But then the mean value theorem implies that there is a $\bar{N}_F \in (N_F^*, N_F^{**})$ such that $\partial_F \pi_F(N_P, \bar{N}_F) = I_F$.
    This is a contradiction, as $\partial_F \pi_F(N_P, N_F) < I_F$ for all $N_F^* < N_F$.
\end{proof}

The intuition behind this result is that \cref{ass:single_crossing} ensures that the total profits achieved by the fringe is either concave or hump-shaped.
Consequently, it has at most one crossing with the -- convex and increasing -- total entry cost function (for $n_F > 0$).
This particular shape (concave or hump-shaped) is also the main driver for the later results about the comparative statics of equilibrium profits and entry.

The following two propositions are partial equilibrium results: consider the number of fringe entrants $N_F$ as fixed.
The first statement claims that the platform's profits are increasing in its own product variety.
\begin{proposition}
    \label{prop:share_of_platform}
    Let \cref{ass:identical_fringe,ass:monotone_profits,ass:profit_sharing} hold.
    Further assume that $f$ is continuously differentiable with respect to $N_P$ and also twice differentiable.
    Let $N_F \geq 0$.
    Then $\pi_P$ is also differentiable and
    \begin{align*}
        \frac{\partial \pi_P(N_P, N_F)}{\partial N_P} > 0.
    \end{align*}
\end{proposition}
\begin{proof}[Proof of \cref{prop:share_of_platform}]
    $f(N_P, N_F)$ is continuously differentiable in $N_P$, therefore the Leibniz rule can be applied to obtain
    \begin{align*}
        \frac{\partial \pi_P(N_P, N_F, N_C)}{\partial N_P} &= N_C \frac{\partial}{\partial N_P} \int_0^1 w_P(s) f(N_P, N_F) \ds \\
        &= \int_0^1 w_P(s) \underbrace{\frac{\partial f(N_P, sN_F)}{\partial N_P}}_{> 0} \ds > 0
    \end{align*}
    for any non-negative, continuous $w_P(s)$.
\end{proof}
While it might seem obvious, let us still examine what this result does and does not mean.
First, remember that $f$ is increasing in both arguments, and $N_F$ is fixed.
Therefore, an increase in $N_P$ also increases the size of the pie the participants bargain over.
This result states that the slice of the pie that the platform gets increases in this case, too.
It does not mean, however, that the \emph{relative share} of the pie that the platform gets is also bigger -- increase is only guaranteed in absolute terms.
For example, it is possible that for the new, higher value of $N_P$, the complementarities between the fringe firms become stronger, and the platform's bargaining power decreases.\footnote{
    In fact, one can show that this is the case if the cross-derivatives of $f$ are negative.
}
\cref{fig:increase_N_P_platform} shows an example of this situation.

@@

Next, let us look at an analogous result for the fringe firms.
In their case, the direction of the change depends on the complementarities between the platform and the fringe firms.
\begin{proposition}
    \label{prop:share_of_fringe}
    Let \cref{ass:identical_fringe,ass:monotone_profits,ass:profit_sharing} hold.
    Furthermore, assume that $f, w$ are twice continuously differentiable.
    Let $N_F > 0$.
    Then $\pi_F$ is also differentiable.
    \begin{align*}
        &\text{If } \frac{\partial^2 f(N_P, n_F)}{\partial n_P \partial n_F} < 0 \;\forall n_F \leq N_F, \text{ then } \frac{\partial \pi_F(N_P, N_F)}{\partial N_P} < 0, \\
        &\text{if } \frac{\partial^2 f(N_P, n_F)}{\partial n_P \partial n_F} > 0 \;\forall n_F \leq N_F, \text{ then } \frac{\partial \pi_F(N_P, N_F)}{\partial N_P} > 0
    \end{align*}
    for all $N_P \geq 0$.
\end{proposition}
\begin{proof}[Proof of \cref{prop:share_of_fringe}]
    Remember that
    \begin{align*}
        \pi_F(N_P, N_F, N_C) = N_C \int_0^1 w_F(s) N_F \partial_2 f(N_P, s N_F) \ds,
    \end{align*}
    By assumption, $f$ is twice continuously differentiable, therefore $\partial_2$ is also continuously differentiable in $N_P$.
    Thus, the Leibniz rule can be applied to obtain
    \begin{align*}
        \frac{\partial \pi_F(N_P, N_F, N_C)}{\partial N_P} &= \frac{\partial}{\partial N_P} N_C \int_0^1 w_F(s) N_F \partial_2 f(N_P, s N_F) \ds \\
        &= N_C \int_0^1 w_F(s) N_F \frac{\partial}{\partial N_P} \partial_2 f(N_P, s N_F) \ds \\
        &= N_C \int_0^1 w_F(s) N_F \partial^2_{12} f(N_P, s N_F) \ds.
    \end{align*}

    As $w_F(s) \geq 0$ for $s > 0$, if $\partial_2 f(N_P, s N_F)$ has the same sign over $[0, N_F]$, then the integral also has the same sign.
    Formally,
    \begin{align*}
        \forall n_F \in [0, N_F] \enspace \frac{\partial^2 f(N_P, n_F)}{\partial N_P \partial n_F} < 0 &\implies \frac{\partial \pi_F(N_P, N_F, N_C)}{\partial N_P} < 0 \\
        \forall n_F \in [0, N_F] \enspace \frac{\partial^2 f(N_P, n_F)}{\partial N_P \partial n_F} > 0 &\implies \frac{\partial \pi_F(N_P, N_F, N_C)}{\partial N_P} > 0
    \end{align*}
\end{proof}
In summary, when they are mostly substitutes (the cross-derivatives of $f$ are negative), the fringe's profits decrease as a result of an increase in $N_F$.
The intuition is that, even though the total size of the pie increases, the bargaining power of the fringe deteriorates so much that its share decreases not only in relative, but also in absolute terms (as illustrated in \cref{fig:increase_N_P_fringe}).
On the other hand, when the fringe firms are mostly complements the fringe's profits increase.

@@

Finally, let us turn to equilibrium entry as a function of the platform's product variety.
The previous proposition implies an almost immediate corollary regarding the equilibrium number of fringe entrants.
\begin{corollary}
    \label{cor:fringe_entry}
    Let \cref{ass:identical_fringe,ass:monotone_profits,ass:profit_sharing,ass:free_entrya,ass:single_crossing} hold.
    Furthermore, assume that $f, w$ are twice continuously differentiable.
    Let $N_F^*$ denote the equilibrium number of fringe firms.
    Let us also assume that $N_F^* > 0$, and that
    \begin{align*}
        \frac{\partial^2 f(n_P, n_F)}{\partial n_P \partial n_F} < 0 \quad \forall n_F \leq N_F \\
        \frac{\partial^2 f(n_P, n_F)}{\partial n_F^2} < 0 \quad \forall n_F \leq N_F.
    \end{align*}
    Then the equilibrium number of fringe firms is also differentiable and
    \begin{align*}
        \frac{\partial N_F^*}{\partial N_P} < 0.
    \end{align*}
\end{corollary}
\begin{proof}[Proof of \cref{cor:fringe_entry}]
    \Cref{prop:unique_equilibrium} establishes that if an equilibrium with $N_F > 0$ exists, it is unique.
    Use the implicit function theorem on the equation from \cref{ass:free_entry} to obtain
    \begin{align*}
        \frac{\partial N_F}{\partial N_P} = \frac{\frac{\partial \pi_F(N_P, N_F, N_C)}{\partial N_P}}{I_F - \frac{\partial \pi_F (N_P, N_F, N_C)}{\partial N_F}}
    \end{align*}
    The derivative exists if the above expression is well-defined, i.e. $\frac{\partial \pi_F (N_P, N_F, N_C)}{\partial N_F} \neq I_F$.
    Remember from \cref{prop:share_of_fringe} that the numerator of this expression is negative under the condition $\frac{\partial^2 f(N_P, N_F, N_C)}{\partial N_P \partial N_F}$.
    Now all we need to show to conclude the proof is that
    \begin{align*}
        \frac{\partial \pi_F (N_P, N_F, N_C)}{\partial N_F} < I_F,
    \end{align*}
    which is the statement of \cref{lem:slope_at_eq}.
\end{proof}

That is, the equilibrium number of entrants increases as a response to an increase in $N_P$ if the platform and the fringe firms are complements, and decreases if they are substitutes.
The underlying reason is again the concave or hump-shaped fringe profit function.
If $N_F^*$ is an equilibrium, then fringe profits minus entry costs are strictly positive for all $N_F \leq N_F^*$ and strictly negative for all $N_F > N_F^*$.
Therefore, if an increase in $N_P$ decreases the fringe's profits for every $N_F \geq 0$, equilibrium can be restored by decreasing the number of fringe entrants, (and vice versa for the other case).
This is also related to the concept of strategic complementary and substitutability, which also depends on the cross-derivatives (i.e. the supermodularity or submodularity) of the profit function.

@@

\begin{proposition}
    \label{prop:aggregate_size_additive}
    Let \cref{ass:identical_fringe,ass:monotone_profits,ass:profit_sharing,ass:free_entrya,ass:single_crossing,ass:additive_profit} hold.
    Then
    \begin{align*}
        \frac{\partial N_F^*}{\partial N_P} < -\frac{\alpha}{\beta}.
    \end{align*}
    Furthermore,
    \begin{align*}
        \frac{\partial \Pi(N_P, N_F^*(N_P), N_C)}{\partial N_P} < 0.
    \end{align*}
\end{proposition}
\begin{proof}[Proof of \cref{prop:aggregate_size_additive}]
    Use the implicit function theorem to get the equilibrium number of fringe firms as a function of the platform's product variety:
    \begin{align*}
        \frac{\partial N_F}{\partial N_P} = \frac{\frac{\partial \pi_F(N_P, N_F, N_C)}{\partial N_P}}{I_F - \frac{\partial \pi_F (N_P, N_F, N_C)}{\partial N_F}}.
    \end{align*}
    Remember, that from \cref{lem:slope_at_eq}, and the assumption on the investment cost function we have that $\frac{\partial \pi_F (N_P, N_F, N_C)}{\partial N_F} < I_F$.
    Then, substitute $f(N_P, N_F) = g(\alpha N_P + \beta N_P)$ into $\pi_F$ to get the following fringe profit function:
    \begin{align*}
        \pi_F(N_P, N_F, N_C) = \beta N_C N_F \int_0^1 w_F(s) g'(\alpha N_P + s \beta N_F) \ds.
    \end{align*}
    Differentiate it with respect to $N_P$ and $N_F$ and substitute into the first expression to obtain
    \begin{align*}
        \frac{\partial N_F}{\partial N_P} = \frac{
            \alpha \beta N_C N_P \int_0^1 w_F(s) g''(\alpha N_P + s \beta N_F) \ds
        }{
            \underbracket{I'_F(N_F) - \beta N_C \int_0^1 w_F(s) g'(\alpha N_P + s \beta N_F) \ds}_{(1)} - \underbracket{\beta^2 N_C N_F \int_0^1 w_F(s) s g''(\alpha N_P + s \beta N_F) \ds}_{(2)}.
        }
    \end{align*}
    From \cref{lem:slope_at_eq}, we know that the denominator of this expression is positive.
    Furthermore, the concavity of $g$ implies that expression (2) is also positive.
    Finally, from \cref{prop:share_of_fringe}, we have that the whole expression must be negative.

@@

\section{Bargaining microfoundations and the cooperative game}
This section examines the bargaining assumption from the main text in more detail.
I proceed in two steps.
First, I provides non-cooperative microfoundations for using the cooperative approach in the first place.
Afterwards, I describe the aforementioned cooperative game in full formality, and derive the (weighted) Shapley value of this game.

\subsection{Non-cooperative microfoundations for the bargaining outcome}
\label{sec:bargaining_microfoundation}
